### 2017-10-12 Paper_report.tex
Paper_Report

\documentclass{article}

\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements

\setlength\parindent{0pt} % Removes all indentation from paragraphs

%\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Paper Report} % Title

\author{NGO HO Anh Khoa} % Author name

\begin{document}
\maketitle % Insert the title, author and date

% If you wish to include an abstract, uncomment the lines below
% \begin{abstract}
% Abstract text
% \end{abstract}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{IBM models}
\section{Unsupervised Neural HMMs \citep{Tran16unsupervised}}
\section{What does Attention in NMT pay Attention to ? \citep{Ghader2017what} }
\subsection{Main idea}
This research compares between Attention Models (Non-recurrent attention model and Input-feeding model) and Word soft Alignment.
The result is that their differences depends on the word being generated.
\subsection{How to compare ?}
Higher consistency between Attention and Alignment leading to better translation.

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{Khoa_Alignment_Paper}

%----------------------------------------------------------------------------------------

\end{document}

### 2017-10-13 Paper_report.tex
What does Attention to NMT pay attention

@@
 %----------------------------------------------------------------------------------------
-%	SECTION 1
+%	IBM models
 %----------------------------------------------------------------------------------------
@@
 \section{IBM models}
+
+%----------------------------------------------------------------------------------------
+%	Unsupervised Neural HMMs
+%----------------------------------------------------------------------------------------
+
 \section{Unsupervised Neural HMMs \citep{Tran16unsupervised}}
+
+%----------------------------------------------------------------------------------------
+%	What does Attention in NMT pay Attention to ?
+%----------------------------------------------------------------------------------------
+
 \section{What does Attention in NMT pay Attention to ? \citep{Ghader2017what} }
 \subsection{Main idea}
-This research compares between Attention Models (Non-recurrent attention model and Input-feeding model) and Word soft Alignment.
-The result is that their differences depends on the word being generated.
+This research compares between Attention Models (Non-recurrent attention model/ Global attention and Recurrent attention/ Input-feeding model) and known Word Alignment.
+The result is that their differences depends on the word type being generated.
 \subsection{How to compare ?}
 Higher consistency between Attention and Alignment leading to better translation.
+
+\begin{itemize}
+\item \textbf{Spearman's rank correlation between attention quality} (Attention loss compared known human alignment) \textbf{and translation quality} (Word prediction loss).
+Higher correlation means a closer relationship between translation quality and consistency of attention versus alignment.
+	\begin{itemize}
+	\item Attention loss
+	\item Word prediction loss
+	\end{itemize}
+\item Attention concentration: Entropy of attention distribution (Soft-hard attention problem)
+\end{itemize}
+
+\subsection{Analysis}
+The analysis is based on POS tags experiments.
+\begin{itemize}
+\item Impact of Attention between Non-recurrent (NR) and Recurrent attention (IF): IF has lower AER (Hard attention) and Attention loss (Soft attention).
+\item Translation quality: Consistency between attention and word alignment depends on POS tags. For example,
+	\begin{itemize}
+	\item There is a higher consistency in the case of nouns. However, attention captures other information in the case of verbs.
+	\item Translation quality of Verbs is better than Nouns. It means attention does not follow alignment for translating Verbs.
+	\end{itemize}
+\item Attention concentration: Review the case of Verbs and Nouns.
+	\begin{itemize}
+	\item Nouns have a lower attention entropy (Higher concentration), lower attention loss (Closer to Alignment), which is that attention entropy can be used as a measure of closeness of attention to alignment in the case of nouns
+	\item Verbs have a lower correlation between attention entropy and word prediction loss, which means that attention concentration is not necessary for translating verbs.
+	\end{itemize}
+\item Attention distribution: It shows how a POS tag of target sentence depends on other POS tags of source sentence.
+\end{itemize}
+
+%----------------------------------------------------------------------------------------
+%	What does Attention in NMT pay Attention to ?
+%----------------------------------------------------------------------------------------
+
+\section{Confidence through Attention \citep{Rikters2017confidence}}
+\subsection{Main idea}
 

### 2017-10-17 Paper_report.tex
Confidence through Attention, Word translation without parallel data

@@
 
-\title{Paper Report} % Title
-
-\author{NGO HO Anh Khoa} % Author name
+\title{Paper Report}
+\author{NGO HO Anh Khoa}
 
 \begin{document}
-\maketitle % Insert the title, author and date
+\maketitle
+
+\tableofcontents
+\newpage
 
@@
 % \end{abstract}
+
+\part{Paper report}
 
@@
 \section{Unsupervised Neural HMMs \citep{Tran16unsupervised}}
+\subsection{Main idea}
+This research show how to apply unsupervised hidden Markov model in neural network approach.
 
@@
 	\item Attention loss
-	\item Word prediction loss
-	\end{itemize}
-\item Attention concentration: Entropy of attention distribution (Soft-hard attention problem)
+		\begin{equation}
+		L_{At}(outToken) = - \sum_{inToken} Al(in, out) * log(At(in, out))
+		\end{equation}
+		\begin{itemize}
+		\item Al(in,out): Weight of alignment link between input token and output token
+		\item At(in,out): Weight of attention between input token and output token
 		\end{itemize}
 
+	\item Word prediction loss: Softmax()
+	\end{itemize}
+
+\item Attention concentration: Entropy of attention distribution (Soft-hard attention problem)
+	\begin{equation}
+	E_{At}(outToken) = - \sum_{in} At(in, out) * log (At(in, out))
+	\end{equation}
+	\begin{itemize}
+	\item At(in,out): Weight of attention between input token and output token
+	\end{itemize}
+\end{itemize}
 \subsection{Analysis}
@@
 \section{Confidence through Attention \citep{Rikters2017confidence}}
+
 \subsection{Main idea}
+\textbf{Auto-evaluation metric without reference.}
+This research is that attention distribution becomes a confidence metric (Translation quality and Decoder confidence)
+\begin{itemize}
+\item Filtering out bad translation from a large back-translated corpus (Provide a better parallel corpus)
+\item Selecting the best translation in a hybrid setup of 2 translation systems
+\end{itemize}
+The result is that this metric could be consider as an human judgement (Not so true!, just about 50\%) and leads to BLEU score improvement (in some cases).
+
+\subsection{How to calculate Confidence metric ?}
+Penalty measures: Coverage deviation and Absentmindedness
+\begin{itemize}
+\item Coverage Deviation Penalty: Lacking attention and Too much attention per input token, which mean penalizing the sum of attention per input token for going to far from 1.0 (Why 1.0: Replaced by token's expected fertility)
+
+\begin{equation}
+CDP = -\frac{1}{inSentLen}\sum_{inToken} log(1 + (1 - \sum_{outToken} \alpha_{out-inToken})^2 )
+\end{equation}
+
+\item Absentmindedness Penalty (Entropy): The attention of confident output tokens should concentrate on a small number of input tokens and vice versa (Assumption).
+\begin{equation}
+AP_{out} = -\frac{1}{inSentLen}\sum_{inToken} \sum_{outToken} \alpha_{out-inToken} * log (\alpha_{out-inToken})
+\end{equation}
+
+\item Combination:
+\begin{equation}
+Confidence = CDP + AP_{out} + AP_{in}
+\end{equation}
+\end{itemize}
+
+\subsection{Analysis}
+\subsubsection{Comparison with human evaluation}
+They use Kendall rank correlation coefficient for looking at the pairs where human scores differ.
+They recognize that their metric over-penalizes the translations which do not follow the source word-by-word.
+\subsubsection{Exp: Filtering Back-translated Data}
+They compare their confidence metric with language model method in filtering the best translated sentences.
+Both methods have the similar levels of overlapping the human evaluation.
+One point should be considered is that their metric does not require any additional model (LM).
+
+For BLEU score, their method show a better performance on some cases, which is in general insignificant.
+
+\subsubsection{Exp: Hybrid Decisions}
+The difference between two baseline systems influences on the final BLEU score.
+A small difference leads to the small improvements, a large difference causes a score drop.
+It is well-reported that hybrid selection overlaps about 50\% human selection.
+
+%----------------------------------------------------------------------------------------
+%	Word Translation without Parallel data
+%----------------------------------------------------------------------------------------
+
+\section{Word Translation without Parallel data \citep{Conneau2017Word}}
+
+\subsection{Main idea}
+The research is about \textbf{building a bilingual dictionary without parallel data} by aligning monolingual word embedding spaces in a unsupervised way (GAN) and proposing a similarity metric CSLS.
+
+Its results show a strong performance of using Procrustes-CSLS. GAN in this case is a step necessary to overcome unsupervised learning.
+
+\subsection{How does it works ?}
+Input: Two large monolingual corpora.\\
+Output: Linear mapping W between the source and target space.
+Two steps of training:
+\begin{enumerate}
+\item Training GAN:
+	\begin{itemize}
+	\item A discriminator distinguishes between n mapped source embeddings and m mapped target embeddings.\\
+	Objective function:
+	\begin{equation}
+	Loss_{D}(\theta_{D}| W) = - \frac{1}{n} \sum_{i=1}^{n} \log P_{\theta_{D}}(source=true|Wx_{i}) - \frac{1}{m} \sum_{i=1}^{m} \log P_{\theta_{D}}(source=false|y_{i})
+	\end{equation}
+
+	\item A generator creates these embeddings to fool discriminator.\\
+	Objective function:
+	\begin{equation}
+	Loss_{W}(W|\theta_{D}) = - \frac{1}{n} \sum_{i=1}^{n} \log P_{\theta_{D}}(source=false|Wx_{i}) - \frac{1}{m} \sum_{i=1}^{m} \log P_{\theta_{D}}(source=true|y_{i})
+	\end{equation}
+
+	\item Update parameter:\\
+	Orthogonality advantages: Reservation of monolingual quality of the embeddings (Dot product of vectors or distances, rotation $\rightarrow$ An isometry of the Euclidean space); Stable training)
+	\begin{equation}
+	W \leftarrow (1 + \beta)W - \beta(WW^{T})W
+	\end{equation}
+
+	\end{itemize}
+\item Refinement procedure (Solution for rare words that GAN does not well solve) repeats until reaching stopping condition.
+	\begin{enumerate}
+	\item Extracting a synthetic high-quality dictionary (Most frequent words) evaluated by CSLS
+	\item Applying Procrustes solution for generating more accurate dictionary.
+	\end{enumerate}
+\item Stopping condition/Best hyper-parameters selection - Validation step: Similarity measure CSLS between mapped source and target words.\\
+	Why: It is based on K-NN and overcomes a problem of two spaces and "Hubs and Anti-hubs" (Some points are highly near many other points while there are some points are not nearest any point in high-dimensional spaces).\\
+	They proposed a bipartite neighbourhood graph. Each word of a language is connected to K words of an other language.
+	\begin{equation}
+	CSLS(Wx_{s}, y_{t}) = 2 \cos(Wx_{s}, y_{t}) - r_{T}(Wx_{s}) - r_{S}(y_{t})
+	\end{equation}
+		\begin{itemize}
+		\item $r_{T}(Wx_{s}) = \frac{1}{K} \sum_{y_{t} \in N_{T}(Wx_{s})} \cos(Wx_{s}, y_{t})$\\
+		Mean similarity of a source embedding $x_{s}$ to its target neighbours.
+		\item $r_{S}(y_{t}) = \frac{1}{K} \sum_{Wx_{s} \in N_{S}(y_{t})} \cos(y_{t}, Wx_{s})$\\
+		Mean similarity of a source embedding $x_{s}$ to its target neighbours.
+		\item $N_{T}(Wx_{s})$: Neighbour of a source word $Wx_{s}$ in target word space.
+		\end{itemize}
+
+\end{enumerate}
+
+%----------------------------------------------------------------------------------------
+%	Report
+%----------------------------------------------------------------------------------------
+\pagebreak 
+\part{Report}
+
+\section{Evaluation of a translation/alignment}
+\begin{enumerate}
+\item Alignment error rate
+\item Attention concentration: Entropy \citep{Ghader2017what}, Absentmindedness penalty \citep{Rikters2017confidence}
+\item Attention loss: Compared with known soft alignment
+\item Confidence metric - Auto-evaluation: Coverage deviation penalty and Absentmindedness penalty \citep{Rikters2017confidence}
+
+\end{enumerate}
 
@@
 %----------------------------------------------------------------------------------------
+\pagebreak 
 \bibliographystyle{plain}

### 2017-10-18 Paper_report.tex
Unupervised Neurall HMM
Unsupervised Neural HMM

@@
 This research show how to apply unsupervised hidden Markov model in neural network approach.
+In fact, they would like to prove that a simple nn models trained to maximize the marginal likelihood could outperform more complicated models in unsupervised learning.
+
+\subsection{What is their concentration ?}
+\begin{itemize}
+\item There are three components:
+	\begin{itemize}
+	\item Set of latent variables Z (Tags)
+	\item Set of observed variables X (Words)
+	\item Model parameters $\theta$ (Emission and transitions probability)
+	\end{itemize}
+
+\item Purpose: Find $\theta$ which maximize p(X $|\theta$)
+\item How: Use Generalized EM to estimate $\theta$
+	\begin{enumerate}
+	\item : Maximizing $p(X)$ means
+	\begin{equation}
+	p(x) = \sum_{z} p(X,Z) = E_{q(Z)}[\ln p(X,Z|\theta)] + H[q(Z)] + KL(q(Z) || p(Z|X,\theta))
+	\end{equation}
+	\item E-step: Estimate $p(Z|X)$ based on current $\theta$
+	\item M-step: Consider $q(Z) = p(Z|X)$ \\
+	$KL(q(Z) || p(Z|X,\theta)) = 0$ \\
+	$H[q(Z)]$ constant
+	\item Maximizing $p(X)$ becomes maximizing $E_{q(Z)}[\ln p(X,Z|\theta)]$
+	\end{enumerate}
+\item Result: Gradient of the joint probability scaled by the posteriors
+	\begin{equation}
+	J(\theta) = \sum_{Z} p(Z|X) \dfrac{\partial}{\partial\theta} \ln p(X,Z| \theta)
+	\label{GradientJointProbability} 
+	\end{equation}
+\item Problem: How to calculate $p(X,Z)$ ?
+\end{itemize}
+
+\subsection{What is the role of HMM ?}
+\begin{itemize}
+\item Assumption:
+	\begin{itemize}
+	\item Every word token is generated by a latent class (Tag)
+	\item The current class at time t is conditioned on the previous class at time (t - 1)
+	\end{itemize}
+
+\item Therefore, the probability of a given sequence of observation X and latent variables Z (Factorization of the joint probability):
+	\begin{equation}
+	p(X,Z) = \prod_{t=1}^{n + 1} p(z_{t}|z_{t-1})\prod_{t=1}^{n} p(x_{t}|z_{t})
+	\label{ProbabilityHMM}
+	\end{equation}
+
+\item Result: Combine $p(X,Z)$ \eqref{ProbabilityHMM} and gradient $J(\theta)$ \eqref{GradientJointProbability}
+
+$J(\theta) = \sum_{Z} p(Z|X) \dfrac{\partial}{\partial\theta} \ln p(X,Z| \theta)$ \\
+
+$ = \sum_{Z} p(Z|X) \dfrac{\partial}{\partial\theta} \ln [\prod_{t=1}^{n + 1} p(z_{t}|z_{t-1},\theta)\prod_{t=1}^{n} p(x_{t}|z_{t},\theta) ]$ \\
+
+$ = \sum_{Z} p(Z|X) \dfrac{\partial}{\partial\theta}  [\sum_{t=1}^{n + 1} \ln p(z_{t}|z_{t-1},\theta) + \sum_{t=1}^{n} \ln p(x_{t}|z_{t},\theta) ]$
+
+$ = \sum_{t}\sum_{z_{t}} p(z_{t}, z_{t-1}|X) \dfrac{\partial}{\partial\theta} \ln p(z_{t}|z_{t-1},\theta) + p(z_{t}|X) \dfrac{\partial}{\partial\theta} \ln p(x_{t}|z_{t},\theta) $
+
+\begin{equation}
+	J(\theta) = \sum_{t}\sum_{z_{t}} p(z_{t}, z_{t-1}|X) \dfrac{\partial}{\partial\theta} \ln p(z_{t}|z_{t-1},\theta) + p(z_{t}|X) \dfrac{\partial}{\partial\theta} \ln p(x_{t}|z_{t},\theta)
+\end{equation}
+
+\item Problem:
+	\begin{itemize}
+	\item How to calculate $p(z_{t}, z_{t-1}|X)$ and $p(z_{t}|X)$ ? They propose Baum-Welch
+	\item How to calculate $p(z_{t}|z_{t-1},\theta)$ and $p(x_{t}|z_{t},\theta)$ ? They propose Neural Networks
+	\end{itemize}
+\end{itemize}
+
+\subsection{Where is neural network ?}
+\begin{itemize}
+\item Input: A sentence $X = x_{1},..., x_{t},... x_{L_{x}}$, a set of vocabulary $W = w_{1},..., w_{i},... w_{L_{W}}$ a set of tags $Z = z_{1},..., z_{j},... z_{L_{z}}$
+\item Output: $p(z_{t}|z_{t-1},\theta)$ and $p(x_{t}|z_{t},\theta)$ at each time t.
+\item How:
+	\begin{enumerate}
+	\item Embedding X and Z by $\theta$: Vector embedding of W $v_{W}$ (Using CNN - Convolution for Morphology) and vector embedding of Z $v_{Z}$ (Simple feed-forward nn having a lookup table following by a non-linear activation ReLU).
+$v_{W}$ and $v_{Z}$ have the same dimension.
+	\item Calculate $p(x_{t}|z_{t},\theta)$ (Emission matrix): Probability of a word $w_{i}$ in Vocabulary is generated by a tag $z_{j}$ (Do not care about time t).
+	\begin{equation}
+	p(w_{i}|z_{j}) = \frac{exp(v_{z_{j}}^{T}*v_{w_{i}} + b_{i})}{\sum_{w \in W} exp(v_{z_{j}}^{T}*v_{w} + b)}
+	\end{equation}
+
+	\item Calculate $p(z_{t}|z_{t-1},\theta)$ (Transition matrix): Probability of a tag $z_{j}$ at time t is generated by a tag $z_{j'}$ at time (t - 1).\\
+	Input: Vector of word w at $x_{t}$ noted $v_{x_{t}}$. It is query embedding (Using LSTMs) \\
+	Result: Matrix of $L_{z}*L_{z}$ noted T. It means all transition probabilities of each tag at (t - 1) to all tags at time t.\\
+	\begin{equation}
+	T = U^{T}*v_{x_{t}} + b
+	\end{equation}
+	\end{enumerate}
+\end{itemize}
 

### 2017-10-25 Paper_report.tex
IBM models
Papers pdf
Word Alignment Modeling with Context Dependent Deep NN

@@
 %----------------------------------------------------------------------------------------
+IBM models
 
@@
 \item Output: $p(z_{t}|z_{t-1},\theta)$ and $p(x_{t}|z_{t},\theta)$ at each time t.
+
 \item How:
@@
 %----------------------------------------------------------------------------------------
+%	Word Alignment Modeling with Context Dependent Deep Neural Network
+%----------------------------------------------------------------------------------------
+
+\section{Word Alignment Modeling with Context Dependent Deep Neural Network \citep{Yang13word}}
+
+\subsection{Main idea}
+The research describes how to use Context Dependent Deep NN in HMM-based word alignment model.
+This means that bilingual word embedding could capture not only lexical translation and context from surrounding words.
+An example is translating a rare word by using its surrounding words.\\
+It is noted that this version uses a smaller number of parameters than the classic HMM model.
+
+\subsection{How does DNN work in word alignment ?}
+The role of DNN in this paper is learning automatically feature from raw text.
+They start from the factorization of the joint probability \cite{Vogel1996HMM}.
+\begin{equation}
+p(a, e| f) = \prod_{i = 1}^{|e|} P_{lex}(e_{i}|f_{a_{i}}) P_{d}(a_{i}|a_{i-1})
+\end{equation}
+	\begin{itemize}
+	\item Given a sentence pair (e,f) 
+	\item $P_{lex}$: Lexical translation probability, emission probability
+	\item $P_{d}$: HMM alignment probability \cite{Vogel1996HMM}, transition probability.
+The paper has a different notation: $P_{d}(a_{i} - a_{i-1})$ and it is called Jump distance distortion probability (Why: The alignment probability depends only on the jump width $(a_{i} - a_{i-1})$ \cite{Vogel1996HMM}).
+	\end{itemize}
+
+They propose using a score instead of these probabilities because they would like to avoid the softmax normalization step of a large vocabulary. The formula above becomes:
+
+\begin{equation}
+s_{NN}(a|e, f) = \prod_{i = 1}^{|e|} t_{lex}(e_{i},f_{a_{i}}|e,f) t_{d}(a_{i},a_{i-1}|e,f)
+\end{equation}
+	\begin{itemize}
+	\item $f_{a_{i}}$ represents not only this word but the context around this word.
+Surrounding words of both source and target word are input of DNN, which is handling the context of both sides.
+This could reduce the explosion of parameter number.
+\\ In this case, they use fixed length windows surrounding both $e_{i}$ and $f_{j}$.
+	\item $t_{lex}$: Lexical translation score.
+	\begin{equation}
+	t_{lex}(e_{i},f_{j}|e,f) = functions_{NN}(window(e_{i}),window(f_{j}) )
+	\end{equation}
+	\item $t_{d}$: Distortion score.
+	\begin{equation}
+	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1}|window(f_{a_{i-1}})) = functions_{NN}(window(f_{a_{i-1}}))
+	\end{equation}
+	They recognize that this lexicalized distortion does not produce a better alignment. They reverse to the simple version.
+	\begin{equation}
+	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1})
+	\end{equation}
+	\end{itemize}
+
+%----------------------------------------------------------------------------------------
 %	Report

### 2017-11-10 Paper_report.tex
Papers

@@
 %----------------------------------------------------------------------------------------
-IBM models
 
@@
 
+\section{Overview about statistical alignment}
+\subsection{General problem}
+Input:
+\begin{itemize}
+\item A source sentence: $f_1^J = f_1,...,f_j,...f_J$
+\item A target sentence: $e_1^I = f_1,...,f_i,...f_I$
+\end{itemize}
+Output: Alignment map $j \rightarrow i = a_j$
+\begin{itemize}
+\item An alignment: $a_1^J = a_1,...,a_j,...a_J$
+\end{itemize}
+
+\subsubsection{}
+Our work is modelling the relationship between a source sentence and a target sentence. \\
+We start from the view of translation model, which is finding this best translation $e_1^I$ for a source sentence $f_1^J$.
+\begin{equation}
+e_1^I = argmax_{e_1^I} p(e_1^I|f_1^J) = argmax_{e_1^I} \frac{p(f_1^J|e_1^I)p(e_1^I)}{p(f_1^J)}
+\end{equation}
+
+In this case, the translation direction is changed from $p(e_1^I|f_1^J)$ to $p(f_1^J|e_1^I)$. This should be noted while reading alignment papers. \\
+
+From now, the work of translation is modelling $p(f_1^J|e_1^I)$.
+Our work is more complicated by adding an alignment component $a_1^J$ which maps from a source position j to a target position $a_j$ (It could be i, but there is also empty words).
+
+\begin{equation}
+p(f_1^J|e_1^I) = \sum_{a_1^J} p(f_1^J, a_1^J|e_1^I)
+\end{equation}
+
+With the model parameters $\theta$, our main problem becomes $p_{\theta}(f_1^J, a_1^J|e_1^I)$
+
+\subsubsection{Problem of empty word}
+
+\subsection{Hidden Markov Alignment Model}
+The alignment model is re-structured:
+\begin{equation}
+p(f_1^J, a_1^J|e_1^I) = p(J|e_1^I) \prod_{j=1}^J p(f_j, a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
+\end{equation}
+\begin{equation}
+= p(J|e_1^I) \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
+\end{equation}
+
+For this new structure, there are three different probabilities:
+\begin{itemize}
+\item $p(J|e_1^I)$ : Length probability
+\item $p( f_j | f_1^{j-1}, a_j, e_1^I)$ : Lexicon  probability
+\item $p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)$ : Alignment probability
+\end{itemize}
+
+We need some assumptions to put this model into HMM:
+\begin{itemize}
+\item $p( f_j | f_1^{j-1}, a_j, e_1^I) \rightarrow p(f_j | e_{a_j}) $ : The lexicon probability depends only on the word at position $a_j$
+\item $p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I) \rightarrow p(a_j | a_{j-1}, I) $ : The alignment $a_j$ depends on $a_{j - 1}$  (First-order dependence)
+\item $p(J|e_1^I) \rightarrow p(J|I)$ : Simplify this probability (Not because of HMM, it's just simplification)
+\end{itemize}
+
+Therefore, $p(f_1^J, a_1^J|e_1^I)$ is decomposed under these assumptions as follows:
+
+\begin{equation}
+p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
+\end{equation}
+
 \section{Evaluation of a translation/alignment}

### 2017-11-13 Paper_report.tex
Alignment model, NN in Word alignment model

@@
 \part{Paper report}
-
-%----------------------------------------------------------------------------------------
-%	IBM models
-%----------------------------------------------------------------------------------------
-
-\section{IBM models}
 
@@
 
+\subsection{Result}
+
+%----------------------------------------------------------------------------------------
+%	Recurrent Neural Networks for Word Alignment Model
+%----------------------------------------------------------------------------------------
+\section{Recurrent Neural Networks for Word Alignment Model \citep{Tamura14recurrent}}
+
+\subsection{Main idea}
+This research is mainly based on \citep{Yang13word}.
+The difference is that the alignment score is calculated in recurrent approach RNNs, which means that $a_j$ depends on all previous position $a_{0...j-1}$.
+
+\subsection{How does RNNs work in calculating alignment score ?}
+
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+
 %----------------------------------------------------------------------------------------
@@
 
-\section{Overview about statistical alignment}
+\section{Overview about statistical alignment \cite{Och2003Systematic}}
 \subsection{General problem}
@@
 
-\subsubsection{}
+\subsubsection{How to model a word alignment ?}
 Our work is modelling the relationship between a source sentence and a target sentence. \\
@@
 With the model parameters $\theta$, our main problem becomes $p_{\theta}(f_1^J, a_1^J|e_1^I)$
-
-\subsubsection{Problem of empty word}
 
@@
 p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
+\label{AlignmentModelEquation}
 \end{equation}
+
+From this formula, we need to calculate these two components:
+\begin{itemize}
+\item $ p(f | e) $ : Translation probability
+\item $p(a_j | a_{j-1}, I)$ or $p(i | i', I)$ : HMM alignment probability
+\end{itemize}
+
+\subsubsection{Assumption about HMM alignment probability $p(a_j | a_{j-1}, I)$ or $p(i | i', I)$}
+Alignment probability depends on the difference in the alignment positions rather than on the absolute position \cite{Vogel1996HMM}.
+
+\begin{equation}
+p(i | i', I) = \frac{c(i - i')}{\sum_{i''=1}^I c(i'' - i')}
+\end{equation}
+where $c(i - i')$ is non-negative.
+
+\subsubsection{Extension: Empty word in target sentence}
+An source word could give an empty word, which is that each target word has an extra empty word.
+This leads to the length of target sentence being $e_{1}^{2I}$ and the empty word zone being $e_{I+1}^{2I}$.
+The word $e_{i}$ has an empty word $e_{i+I}$.
+
+They enforce the constraints:
+\begin{equation}
+p(i + I | i', I) = p_{0} \delta(i, i')
+\end{equation}
+\begin{equation}
+p(i + I | i' + I, I) = p_{0} \delta(i, i')
+\end{equation}
+\begin{equation}
+p(i | i' + I, I) = p(i | i', I )
+\end{equation}
+
+where $p_{0}$ is the probability of a transition to the empty word.
+
+\subsubsection{Extension: Refinement of alignment}
+
+\begin{itemize}
+\item Purpose: Add more assumptions that $p(a_j | a_{j-1}, I)$ depends on $e_{a_{j -1}}$ or $f_j$.
+\item Problem: In the case of large corpora or large size of vocabulary, it leads to a large alignment parameters.
+\item Solution: They use classes G which are the mappings of words to classes.
+\end{itemize}
+
+\section{Word alignment model in Neural Network}
+We start from this formula \ref{AlignmentModelEquation}:
+
+\begin{equation}
+p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
+\end{equation}
+
+In general, we try to calculate these probability by using two different neural networks.
+The significant point of NN is Context.
+
+\subsection{Non-probability approach, we use score}
+The papers include \cite{Yang13word}, \cite{Tamura14recurrent}.
 

### 2017-11-14 Paper_report.tex
Alignment score, non-probability

@@
 	J(\theta) = \sum_{Z} p(Z|X) \dfrac{\partial}{\partial\theta} \ln p(X,Z| \theta)
-	\label{GradientJointProbability} 
+	\label{Tran16unsupervisedGradientJointProbability} 
 	\end{equation}
@@
 	p(X,Z) = \prod_{t=1}^{n + 1} p(z_{t}|z_{t-1})\prod_{t=1}^{n} p(x_{t}|z_{t})
-	\label{ProbabilityHMM}
+	\label{Tran16unsupervisedProbabilityHMM}
 	\end{equation}
 
-\item Result: Combine $p(X,Z)$ \eqref{ProbabilityHMM} and gradient $J(\theta)$ \eqref{GradientJointProbability}
+\item Result: Combine $p(X,Z)$ \eqref{Tran16unsupervisedProbabilityHMM} and gradient $J(\theta)$ \eqref{Tran16unsupervisedGradientJointProbability}
 
@@
 s_{NN}(a|e, f) = \prod_{i = 1}^{|e|} t_{lex}(e_{i},f_{a_{i}}|e,f) t_{d}(a_{i},a_{i-1}|e,f)
+\label{Yang13wordNNAlignmentScore}
 \end{equation}
+
 	\begin{itemize}
+	\item $s_{NN}(a|e, f)$ is the score of an alignment based on the source and target sentence.
 	\item $f_{a_{i}}$ represents not only this word but the context around this word.
@@
 	t_{lex}(e_{i},f_{j}|e,f) = functions_{NN}(window(e_{i}),window(f_{j}) )
+	\label{Yang13wordLexicalTranslationScore}
 	\end{equation}
@@
 
-\subsection{Result}
+\subsection{Loss in supervised learning}
+\begin{equation}
+loss(\theta) = \sum_{every(\textbf{e},\textbf{f})} \max(0 , 1 - s_{\theta}(a^+ |\textbf{e},\textbf{f}) + s_{\theta}(a^- |\textbf{e},\textbf{f}) )
+\label{Yang13wordAlignmentLoss}
+\end{equation}
+where
+\begin{itemize}
+\item $a^+$: Gold alignment path
+\item $a^-$: Highest scoring incorrect alignment path under $\theta$
+\item $s_\theta$: Score for alignment path defined in \eqref{Yang13wordNNAlignmentScore}
+\end{itemize}
+
+\subsection{Analysis}
+\subsubsection{Two loss functions during training}
+They pre-train word embedding with monolingual data.
+They train firstly NN with the loss from lexical translation score and then the loss \eqref{Yang13wordAlignmentLoss} because they recognize that using only the loss \eqref{Yang13wordAlignmentLoss} is not efficient.
+
+The loss of lexical translation score:
+\begin{equation}
+loss(\theta) = \sum_{every(\textbf{e},\textbf{f})} \max(0 , 1 - t_{lex, \theta}((e,f)^+ | \textbf{e},\textbf{f}) + t_{lex, \theta}((e,f)^- | \textbf{e},\textbf{f}) )
+\end{equation}
+where
+\begin{itemize}
+\item $(e,f)^+$: Correct word pair
+\item $(e,f)^-$: Incorrect word pair
+\item $t_{lex}$: Score of \eqref{Yang13wordLexicalTranslationScore}
+\end{itemize}
+
+\subsubsection{Result}
+Baselines are HMM and IBM4. IBM4+NN takes the first place, followed by IBM4 and then HMM+NN.
+
+\subsubsection{Notes}
+They conclude also that the size of window influence on the accuracy of translation score.
+The large number of hidden layer does not return any improvement.
 
@@
 This research is mainly based on \citep{Yang13word}.
-The difference is that the alignment score is calculated in recurrent approach RNNs, which means that $a_j$ depends on all previous position $a_{0...j-1}$.
+The difference is that the score of alignment is calculated in recurrent approach RNNs, which means that $a_j$ depends on all previous position $a_{0...j-1}$.
+The score of an alignment in \citep{Yang13word} has two components: One is for lexical translation and the other is for alignment. This research proposes a single score.
 
 \subsection{How does RNNs work in calculating alignment score ?}
+
+The equation of \citep{Yang13word} (Reverse the source and the target sentence)
+\begin{equation}
+s_{NN}(a_1^ J|e_1^ I, f_1^ J) = \prod_{j = 1}^{J} t_{d}(a_{j},a_{j-1}|window(e_{a_{j-1}})) *t_{lex}(f_{j},e_{a_{j}}|window(e_{a_{j}}), window(f_{j}))
+\end{equation}
+
+It is modified for RNNs:
+
+\begin{equation}
+s_{NN}(a_1^ J|e_1^ I, f_1^ J) = \prod_{j = 1}^{J} t_{RNN}(a_{j}|a_1^{j-1},e_{a_{j}},f_j  )
+\end{equation}
+
+\subsection{Loss in unsupervised learning} 
+\begin{equation}
+loss(\theta) = max(0 , 1 - \sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]  + \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )
+\label{Tamura14recurrentLossUnsupervisedLearning}
+\end{equation}
+where
+\begin{itemize}
+\item T: Training data (Bilingual sentences) as Observed data
+\item $\Omega$ : Full translation search space as neighbourhood of observe data, .
+\item $\Phi$ : Set of all possible alignments given (\textbf{e},\textbf{f})
+\item $E_{\Phi} [s_{\theta}]$ : Expected value of the scores $s_\theta$ on $\Phi$
+\item $e^+$ : A target language sentence in T
+\item $e^-$ : A pseudo-target language sentence
+\item $\sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]$ : Expectation term for observed data
+\item$ \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )$ : Expectation term for neighbourhood
+\end{itemize}
+
+They would like to reduce the computation, they randomly select N pseudo-target language sentences for each $f^+$. \eqref{Tamura14recurrentLossUnsupervisedLearning} becomes:
+\begin{equation}
+loss(\theta) = \sum_{\textbf{f}^+ \in T} max(0 , 1 -  E_{GEN} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]  + \frac{1}{N} \sum_{\textbf{e}^-} E_{GEN} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )
+\end{equation}
+where
+\begin{itemize}
+\item $\textbf{e}^-$ : a pseudo-target language sentence with the same length $|\textbf{e}^-| = |\textbf{e}^+|$
+\item GEN: A subset of all possible alignment generated by beam search
+\end{itemize}
+
+\subsection{Agreement constraints} 
+\subsection{Analysis}
 
@@
 
-\section{Overview about statistical alignment \cite{Och2003Systematic}}
-\subsection{General problem}
+\section{Overview about statistical alignment }
+
+\subsection{Word-based alignment ? \cite{Och2003Systematic}}
 Input:
@@
 
-\subsubsection{How to model a word alignment ?}
 Our work is modelling the relationship between a source sentence and a target sentence. \\
@@
 p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
-\label{AlignmentModelEquation}
+\label{Och2003SystematicAlignmentModelEquation}
 \end{equation}
@@
 \section{Word alignment model in Neural Network}
-We start from this formula \ref{AlignmentModelEquation}:
+We start from this formula \eqref{Och2003SystematicAlignmentModelEquation}:
 
@@
 
-\subsection{Non-probability approach, we use score}
+\subsection{Probability approach}
+The papers include \cite{Tran16unsupervised}.
+
+\subsection{Non-probability - Score approach}
 The papers include \cite{Yang13word}, \cite{Tamura14recurrent}.

### 2017-11-16 Paper_report.tex
Save

@@
 	J(\theta) = \sum_{Z} p(Z|X) \dfrac{\partial}{\partial\theta} \ln p(X,Z| \theta)
-	\label{Tran16unsupervisedGradientJointProbability} 
+	\label{Tran16unsupervised Gradient Joint Probability} 
 	\end{equation}
@@
 	p(X,Z) = \prod_{t=1}^{n + 1} p(z_{t}|z_{t-1})\prod_{t=1}^{n} p(x_{t}|z_{t})
-	\label{Tran16unsupervisedProbabilityHMM}
+	\label{Tran16unsupervised Probability HMM}
 	\end{equation}
 
-\item Result: Combine $p(X,Z)$ \eqref{Tran16unsupervisedProbabilityHMM} and gradient $J(\theta)$ \eqref{Tran16unsupervisedGradientJointProbability}
+\item Result: Combine $p(X,Z)$ \eqref{Tran16unsupervised Probability HMM} and gradient $J(\theta)$ \eqref{Tran16unsupervised Gradient Joint Probability}
 
@@
 %----------------------------------------------------------------------------------------
+%	Alignment by agreement
+%----------------------------------------------------------------------------------------
+\section{Alignment by Agreement \citep{Liang2006Alignment}}
+
+%----------------------------------------------------------------------------------------
 %	Word Alignment Modeling with Context Dependent Deep Neural Network
@@
 s_{NN}(a|e, f) = \prod_{i = 1}^{|e|} t_{lex}(e_{i},f_{a_{i}}|e,f) t_{d}(a_{i},a_{i-1}|e,f)
-\label{Yang13wordNNAlignmentScore}
+\label{Yang13word NN Alignment Score}
 \end{equation}
@@
 	t_{lex}(e_{i},f_{j}|e,f) = functions_{NN}(window(e_{i}),window(f_{j}) )
-	\label{Yang13wordLexicalTranslationScore}
+	\label{Yang13word Lexical Translation Score}
 	\end{equation}
@@
 loss(\theta) = \sum_{every(\textbf{e},\textbf{f})} \max(0 , 1 - s_{\theta}(a^+ |\textbf{e},\textbf{f}) + s_{\theta}(a^- |\textbf{e},\textbf{f}) )
-\label{Yang13wordAlignmentLoss}
+\label{Yang13word Alignment Loss}
 \end{equation}
@@
 \item $a^-$: Highest scoring incorrect alignment path under $\theta$
-\item $s_\theta$: Score for alignment path defined in \eqref{Yang13wordNNAlignmentScore}
+\item $s_\theta$: Score for alignment path defined in \eqref{Yang13word NN Alignment Score}
 \end{itemize}
@@
 They pre-train word embedding with monolingual data.
-They train firstly NN with the loss from lexical translation score and then the loss \eqref{Yang13wordAlignmentLoss} because they recognize that using only the loss \eqref{Yang13wordAlignmentLoss} is not efficient.
+They train firstly NN with the loss from lexical translation score and then the loss \eqref{Yang13word Alignment Loss} because they recognize that using only the loss \eqref{Yang13word Alignment Loss} is not efficient.
 
@@
 \item $(e,f)^-$: Incorrect word pair
-\item $t_{lex}$: Score of \eqref{Yang13wordLexicalTranslationScore}
+\item $t_{lex}$: Score of \eqref{Yang13word Lexical Translation Score}
 \end{itemize}
@@
 loss(\theta) = max(0 , 1 - \sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]  + \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )
-\label{Tamura14recurrentLossUnsupervisedLearning}
+\label{Tamura14recurrent Loss Unsupervised Learning}
 \end{equation}
@@
 
-They would like to reduce the computation, they randomly select N pseudo-target language sentences for each $f^+$. \eqref{Tamura14recurrentLossUnsupervisedLearning} becomes:
+They would like to reduce the computation, they randomly select N pseudo-target language sentences for each $f^+$. \eqref{Tamura14recurrent Loss Unsupervised Learning} becomes:
 \begin{equation}
@@
 \subsection{Agreement constraints}
+\marginpar{See \citep{Liang2006Alignment}}
+
+Why: HMM-based model is asymmetric. It is demonstrated that encouraging directional models to agree improves alignment performance.
+\\
+How: They propose training two directional models including alignment F$\rightarrow$E and E$\rightarrow$F. Each model has a different modified loss function
+
+\begin{equation}
+loss_{\theta_{F \rightarrow E}} = loss(\theta_{F \rightarrow E})  + \alpha \parallel \theta_{E \rightarrow F} - \theta_{F \rightarrow E} \parallel
+\end{equation}
+
+\begin{equation}
+loss_{\theta_{E \rightarrow F}} = loss(\theta_{E \rightarrow F})  + \alpha \parallel \theta_{F \rightarrow E} - \theta_{E \rightarrow F} \parallel
+\end{equation}
+
+where
+\begin{itemize}
+\item $\theta_{E \rightarrow F}$ : Weight of layers in model $E \rightarrow F$
+\item $\alpha$: Weight parameter of the agreement constraint $\parallel \theta_{E \rightarrow F} - \theta_{F \rightarrow E} \parallel$
+\item $\parallel \theta \parallel$: Norm of $\theta$
+\item $loss(\theta_{F \rightarrow E})$: Loss from \eqref{Tamura14recurrent Loss Unsupervised Learning}
+\end{itemize}
+
 \subsection{Analysis} 
+Baselines are IBM4, FFNN \citep{Yang13word}. They do the experiments of word alignment and machine translation in both unsupervised/supervised learning.
+
+\subsubsection{Result}
+RNNs captures alignment paths based on long alignment history.
+This can be viewed as phrase-level alignment, which is more effective in non-similar-order-language (Japanese-English) than French-English.\\
+
+RNNs could help to reduce the size of training data. They show the similar results between RNNs-Small data and IBM4-Large data.\\
+
+They highlight the role of agreement constraints in alignment performance improvement.\\
 
@@
 
-\subsection{Hidden Markov Alignment Model}
+\subsection{Hidden Markov Alignment Model \cite{Och2003Systematic}}
 The alignment model is re-structured:
@@
 p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
-\label{Och2003SystematicAlignmentModelEquation}
+\label{Och2003Systematic Alignment Model Equation}
 \end{equation}
@@
 \section{Word alignment model in Neural Network}
-We start from this formula \eqref{Och2003SystematicAlignmentModelEquation}:
+We start from this formula \eqref{Och2003Systematic Alignment Model Equation}:
 
@@
 p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
+\label{Word Alignment Model Neural Network HMM Equation}
 \end{equation}
@@
 In general, we try to calculate these probability by using two different neural networks.
-The significant point of NN is Context.
+The significant point of NN is embedding context.
 
 \subsection{Probability approach}
-The papers include \cite{Tran16unsupervised}.
+Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM. \eqref{Word Alignment Model Neural Network HMM Equation} becomes:
+\begin{equation}
+p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
+\end{equation}
 
 \subsection{Non-probability - Score approach}
-The papers include \cite{Yang13word}, \cite{Tamura14recurrent}.
+The papers are \cite{Yang13word}, \cite{Tamura14recurrent}.
+
+\section{Techniques in Alignment}
+
+\subsection{Agreement between models}
 

### 2017-11-16 Paper_report.tex
save

@@
 \begin{equation}
-p(f_1^J|e_1^I) = \sum_{a_1^J} p(f_1^J, a_1^J|e_1^I)
 \end{equation}
@@
 With the model parameters $\theta$, our main problem becomes $p_{\theta}(f_1^J, a_1^J|e_1^I)$
+
+\begin{equation}
+p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)
+\label{Overview about Statistical Alignment p(f,e)}
+\end{equation}
 
@@
 \section{Word alignment model in Neural Network}
-We start from this formula \eqref{Och2003Systematic Alignment Model Equation}:
+We start from this formula \eqref{Overview about Statistical Alignment p(f,e)}:
 
 \begin{equation}
-p(f_1^J, a_1^J|e_1^I) = p(J|I) \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
-\label{Word Alignment Model Neural Network HMM Equation}
+p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)
+\label{Word Alignment Model Neural Network p(f,e)}
 \end{equation}
 
-In general, we try to calculate these probability by using two different neural networks.
-The significant point of NN is embedding context.
+\subsection{Probability approach}
+Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM.
+In general, we try to calculate the probability by using two different neural networks.The significant point of NN is embedding context.
 
-\subsection{Probability approach}
-Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM. \eqref{Word Alignment Model Neural Network HMM Equation} becomes:
-\begin{equation}
-p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1}, I)
-\end{equation}
+They use Generalized EM to estimate $\theta$, \eqref{Word Alignment Model Neural Network p(f,e)} becomes:
+
+$p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)$ \\
+
+$ = E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ] + H[q(a_1^J)] + KL(q(a_1^J) \| p_{\theta}(a_1^J|f_1^J,e_1^I) ) $ \\
+
+Updating $\theta$ requires only maximizing $E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ]$. The gradient is: \\
+\marginpar{Why?: See \citep{Tran16unsupervised}}
+
+$ J(\theta) = \sum_{a_1^J} \quad q(a_1^J)\quad ln \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $
 

### 2017-11-18 Paper_report.tex
HMM Unsupervised for MT

@@
 \subsection{Probability approach}
+\subsubsection{\cite{Tran16unsupervised}}
 Unsupervised neural HMM of \cite{Tran16unsupervised} shows how to apply NN in HMM.
@@
 
-They use Generalized EM to estimate $\theta$, \eqref{Word Alignment Model Neural Network p(f,e)} becomes:
+\begin{enumerate}
+\item They use Generalized EM to estimate $\theta$, \eqref{Word Alignment Model Neural Network p(f,e)} becomes:\\
 
-$p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)$ \\
+$p_{\theta}(f_1^J|e_1^I) = \sum_{a_1^J} p_{\theta}(f_1^J, a_1^J|e_1^I)$
 
-$ = E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ] + H[q(a_1^J)] + KL(q(a_1^J) \| p_{\theta}(a_1^J|f_1^J,e_1^I) ) $ \\
+$ = E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ] + H[q(a_1^J)] + KL(q(a_1^J) \| p_{\theta}(a_1^J|f_1^J,e_1^I) ) $
 
-Updating $\theta$ requires only maximizing $E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ]$. The gradient is: \\
+\item Updating $\theta$ requires only maximizing $E_{q(a_1^J)} [ln p_{\theta}(f_1^J, a_1^J|e_1^I) ]$. \\ The gradient is: \\
 \marginpar{Why?: See \citep{Tran16unsupervised}}
 
-$ J(\theta) = \sum_{a_1^J} \quad q(a_1^J)\quad ln \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $
+$ J(\theta) = \sum_{a_1^J} \quad q(a_1^J)\quad \bigtriangledown log \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $
+
+\item In the step E, we model $q(a_1^J) = p_{\theta'}(a_1^J|f_1^J,e_1^I)$.
+Therefore,\\
+
+$ J(\theta) = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown log \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $
+
+\item From \eqref{Och2003Systematic Alignment Model Equation}, we have \\
+$p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j | e_{a_j}) * p(a_j | a_{j-1})$  with the assumptions about I, J.
+Therefore, \\
+
+$ J(\theta) = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown log \, p_{\theta}(f_1^J, a_1^J|e_1^I)  $
+
+$ = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown log \, [\prod_{j=1}^J p_{\theta}(f_j | e_{a_j}) * p_{\theta}(a_j | a_{j-1})  ] $
+
+$ = \sum_{a_1^J} \quad p_{\theta'}(a_1^J|f_1^J,e_1^I) \quad \bigtriangledown [\sum_{j=1}^J log \, p_{\theta}(f_j | e_{a_j}) + log \, p_{\theta}(a_j | a_{j-1})  ] $
+
+$ = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j,e_{a_j}) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j,e_{a_j}) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ] $
+
+\item We choose $a$ is state, $f$ is observation. We remove $e$.
+Therefore, \\
+
+$ J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ] $
+
+\end{enumerate}
+
+\paragraph{How to apply NN ?}
+\begin{itemize}
+\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities of all source-language vocabulary.
+\item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
+\item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
+\end{itemize}
 

### 2017-11-23 Paper_report.tex
Save

@@
 \section{Alignment by Agreement \citep{Liang2006Alignment}}
+\subsection{Main idea}
+This approach is similar to ensemble method.
+In this unsupervised approach, the two simple asymmetric models are trained jointly to maximize a combination of data likelihood and agreement between the models.
+The new point is encouraging the agreement between these models during training.
+
+In fact, intersecting the alignment prediction of two asymmetric models reduces AER. An assumption is that this intersection (Agreement) could reduce the loss of each asymmetric model.
+
+Moreover, we could see the transformation from asymmetric models to symmetric model.
+
+\subsection{}
 
@@
 \begin{itemize}
-\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities of all source-language vocabulary.
+\item Emission matrix $p_{\theta}(f_j | e_{a_j})$: It is not the normal way of translation. We receive the target-language sentence and return the probabilities for all source-language vocabulary.
 \item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
@@
 
+\paragraph{What is the problem of transition matrix in programming ?}
+The input of transition model is target sentence. The model returns the matrix with its size being ($I * I$).
+
+However, this matrix is hard to return.
+This is why I return matrix ($I * V_e$) with $V_e$ is the size of target language vocabulary.
+From this matrix, I could select the probabilities of the words existed in target sentence.
+The final result is a matrix with its size being ($I * I$).
+
+This method breaks the structure of the tensor tree. The cost calculated can not be back-propagated because there is no relationship between this cost and this matrix ($I * V_e$).
+
 \subsection{Non-probability - Score approach}
-The papers are \cite{Yang13word}, \cite{Tamura14recurrent}.
+\subsubsection{\cite{Yang13word}, \cite{Tamura14recurrent}}
+
+\section{Symmetrical alignment}
 

### 2017-11-27 Paper_report.tex
Hierarchical multiscale recurrent neural networks

@@
 %----------------------------------------------------------------------------------------
+%	Hierarchical Multiscale Recurrent Neural Networks
+%----------------------------------------------------------------------------------------
+
+\section{Hierarchical Multiscale Recurrent Neural Networks}
+
+\subsection{Main idea}
+Hierarchical Multiscale RNNs learns the latent hierarchical structure of a sequence and its temporal representation with non-fixed timescales (Without explicit boundary information).
+
+For example, this model consider a sentence as a list of characters, not only words. It is trained to know autonomously the beginning and the end of a word. For each layer, it could group the units.
+
+The key idea is an update mechanism with a binary boundary detector (Gate determining the boundary of an object).\\
+
+The advantages of "Multiscale" over standard RNNs:
+\begin{itemize}
+\item Updating the high-level layers is less frequently $\rightarrow$ Computational efficiency and Vanishing gradient problem.
+Solving vanishing gradient problem means that this model could delivering efficiently long-term dependencies.
+\item Flexible resource allocation.
+The model could modify the number of hidden units for an information.
+For example, the model could use more units to the higher layers (Long-term dependency) and less units to the lower layers (Short-term dependency).
+This means that it could decide to keep the long-term or short-term information.
+
+\item A good generalization performance (Dropout approach)
+\item The internal process of RNN becomes more interpretable. We could count the number of operation execution time ( Update, Flush and Copy operation)
+\end{itemize}
+
+The problem of the previous kind of RNNs:
+\begin{itemize}
+\item LSTMs: LSTMs has also an update mechanism with forget and update gates, which means that it could operate with different timescales.
+However, these timescales are not organized hierarchically.
+\\
+Problem:
+	\begin{itemize}
+	 \item In practice, after a few hundred time steps, long-term information is gradually diluted at every time step.
+	 \item LSTMs is computationally expensive (Update at every time step for each unit)
+ 	\end{itemize}
+
+\item Clockwork RNNs and its soft timescale approach: The hidden units are grouped into several modules.
+Different timescales are assigned to these modules (i.e: A module $i$ is updated at every $2^{i - 1}$ -th time step).\\
+Problem:
+	\begin{itemize}
+	\item It is not easy to find a good timescales because timescale depends on data.
+	\item It is unclear how to deploy more layers than the number of boundary levels that is explicitly observed in the data.
+	\end{itemize}
+
+\item Hierarchical RNNs with Known explicit hierarchical boundary structure (Not multiscale).\\ Problem: It is the same with Clockwork RNNs that boundary information is not explicit and expensive to be discovered.
+
+\item CNNs with 1-D kernels: It could provide also high-level representation of sequence.\\
+Problem: We need to observe a full sequence with a reduced length.
+
+\item Zoneout, a regularization technique similar to dropout.\\
+Problem: Its strength is still an hyper-parameter.
+
+\end{itemize}
+
+\subsection{Update mechanism}
+They describe Hierarchical Multiscale RNN (HM-RNN) based on LSTM update rule. It is better to see the graph in paper.\\
+\marginpar{Why it is not based on RNN ?}
+
+At each time step $t$, for each layer $l$, there are:
+\begin{equation}
+h_t^l,\, c_t^l,\, z_t^l = f^l (c_{t-1}^l, h_{t-1}^l, h_t^{l-1}, h_{t-1}^{l+1}, z_{t-1}^l, z_t^{l-1})
+\end{equation}
+
+The function includes Update, Copy and Flush operation depending on binary detector - boundary states $z_{t-1}^l$ (Previous time step) and $z_t^{l-1}$ (Below layer).
+The difference between three operations are the use of context $c$ which keeps the summary information of the previous units.
+\begin{itemize}
+\item \textbf{Flush}: It shows the beginning of a segment or "word", the boundary is found previously.
+\\ The unit $h_t^l$ does not get information from same-level context $c_{t-1}^l$ (Eject) but higher-level unit $h_{t-1}^{l+1}$ (This is the connection between two words, it is re-installed with more long-term information from previous words).
+
+\item  \textbf{Copy}: It shows not-end state of a "word", none of boundary is found.
+\\ the unit  $h_t^l$ only copies from previous unit $h_{t-1}^l$, its context copies from $c_{t-1}^l$ (It reduces the number of operation execution, leading to computational efficiency).
+
+\item \textbf{Update}: It is similar to update operation of LSTM (Forget, input and output gate) but it is executed sparsely. It is the end of a "word", the boundary is found in the unit below.
+\\ The unit $h_t^l$ gets also information from the same-level context $c_{t-1}^l$ and information from the lower-level unit $h_t^{l-1}$, but not from the higher-level unit $h_{t-1}^{l+1}$ (It does not need information from previous words).
+\end{itemize}
+
+\subsection{Analysis}
+The result for character-level language model does not show clearly a good performance.
+
+%----------------------------------------------------------------------------------------
 %----------------------------------------------------------------------------------------

### 2017-12-05 Paper_report.tex
Save

@@
 \end{itemize}
-The result is that this metric could be consider as an human judgement (Not so true!, just about 50\%) and leads to BLEU score improvement (in some cases).
+The result is that this metric could be consider as an human judgment (Not so true!, just about 50\%) and leads to BLEU score improvement (in some cases).
 
@@
 	Why: It is based on K-NN and overcomes a problem of two spaces and "Hubs and Anti-hubs" (Some points are highly near many other points while there are some points are not nearest any point in high-dimensional spaces).\\
-	They proposed a bipartite neighbourhood graph. Each word of a language is connected to K words of an other language.
+	They proposed a bipartite neighborhood graph. Each word of a language is connected to K words of an other language.
 	\begin{equation}
@@
 		\item $r_{T}(Wx_{s}) = \frac{1}{K} \sum_{y_{t} \in N_{T}(Wx_{s})} \cos(Wx_{s}, y_{t})$\\
-		Mean similarity of a source embedding $x_{s}$ to its target neighbours.
+		Mean similarity of a source embedding $x_{s}$ to its target neighbors.
 		\item $r_{S}(y_{t}) = \frac{1}{K} \sum_{Wx_{s} \in N_{S}(y_{t})} \cos(y_{t}, Wx_{s})$\\
-		Mean similarity of a source embedding $x_{s}$ to its target neighbours.
-		\item $N_{T}(Wx_{s})$: Neighbour of a source word $Wx_{s}$ in target word space.
+		Mean similarity of a source embedding $x_{s}$ to its target neighbors.
+		\item $N_{T}(Wx_{s})$: Neighbor of a source word $Wx_{s}$ in target word space.
 		\end{itemize}
@@
 
-\subsection{}
+\subsection{How to train these two model ?}
+\begin{itemize}
+\item Two models are:
+\begin{equation}
+\begin{split}
+&p_1(x,z; \theta_1) = p(e)p(a,f| e; \theta_1)  \\
+&p_2(x,z; \theta_2) = p(f)p(a,e| f; \theta_2)
+\end{split}
+\end{equation}
+where \\
+$x = (e,f)$ is an input sentence pair, \\
+$z = {z_{i,j} \in \{0,1\} : 1 \leq i \leq I, 1 \leq j \leq J}$ is a set of indicator variables for each potential alignment edge.
+
+\item The data likelihood:
+\begin{equation}
+\prod_x p_k(x; \theta_k) = \prod_x \sum_z p_k(x,z, \theta_k)
+\end{equation}
+where $k \in {1, 2}$ is models.
+
+\item \textbf{Joint objective function} is maximizing the data likelihood:
+\begin{equation}
+\max_{\theta_1, \theta_2} \sum_x [log p_1(x;\theta_1) + log p_2(x;\theta_2)] \\
+\end{equation}
+Because of the probability that two models agree the alignments on an example $x$ being
+\begin{equation}
+\sum_z p_1(z
+|x;\theta_1) p_2(z|x; \theta_2)
+\end{equation}
+
+\item Therefore,
+\begin{equation}
+\max_{\theta_1, \theta_2} \sum_x [log p_1(x;\theta_1) + log p_2(x;\theta_2) + log\sum_z p_1(z
+|x;\theta_1) p_2(z|x; \theta_2)]
+\end{equation}
+\end{itemize}
+
+\subsubsection{Optimization via EM}
+From the standard EM,
+\begin{equation}
+\begin{split}
+& E: q(z;x) := p(z|x ;\theta) \\
+& M: \theta^{'} := argmax_{\theta} \sum_{x,z} q(z;x) \quad log \,  p(x,z;\theta)
+\end{split}
+\end{equation}
+
+becomes
+
+\begin{equation}
+\begin{split}
+& E: q(z;x) := \frac{1}{Z_x} p_1(z|x ;\theta_1) p_2(z|x ;\theta_2) \\
+& M: \theta^{'} := argmax_{\theta} \sum_{x,z} q(z;x) \, log \,  p_1(x,z;\theta_1) +  \sum_{x,z} q(z;x) \, log \,  p_2(x,z;\theta_2)
+\end{split}
+\end{equation}
+
+where $Z_x$ is a normalization constant. It is sum of the product of two model posteriors over the set of possible $z$ with nonzero probability under both models.\\
+
+In E-step,
+\begin{equation}
+ E: q(z;x) := \frac{1}{Z_x} p_1(z|x ;\theta_1) p_2(z|x ;\theta_2)
+\end{equation}
+
+becomes
+
+\begin{equation}
+q(z;x) := \prod_{i,j} p_1(z_{ij} | x; \theta_1) \, p_2(z_{ij} | x; \theta_2)
+\end{equation}
+where each $p_k(z_{i,j}|x; \theta_k)$ is the posterior marginal probability of the (i,j) edge.\\
+
+This posterior $q(z;x)$ could show the disagreement because this product $p_1(z|x ;\theta_1) p_2(z|x ;\theta_2)$ is small.
+
+\subsection{Analysis}
+This agreement approach does not guarantee to increase the joint objective.
+The experiment shows that it could provide an effective method of achieving model agreement and a significant accuracy gains over independent training.
 
@@
 \item T: Training data (Bilingual sentences) as Observed data
-\item $\Omega$ : Full translation search space as neighbourhood of observe data, .
+\item $\Omega$ : Full translation search space as neighborhood of observe data, .
 \item $\Phi$ : Set of all possible alignments given (\textbf{e},\textbf{f})
@@
 \item $\sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]$ : Expectation term for observed data
-\item$ \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )$ : Expectation term for neighbourhood
+\item$ \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )$ : Expectation term for neighborhood
 \end{itemize}
@@
 
-\section{Hierarchical Multiscale Recurrent Neural Networks}
+\section{Hierarchical Multiscale Recurrent Neural Networks \citep{Chung2016Hierarchical}}
 
 \subsection{Main idea}
-Hierarchical Multiscale RNNs learns the latent hierarchical structure of a sequence and its temporal representation with non-fixed timescales (Without explicit boundary information).
+Hierarchical Multi-scale RNNs learns the latent hierarchical structure of a sequence and its temporal representation with non-fixed timescales (Without explicit boundary information).
 
@@
 
-The advantages of "Multiscale" over standard RNNs:
+The advantages of "Multi-scale" over standard RNNs:
 \begin{itemize}
@@
 
-\item Hierarchical RNNs with Known explicit hierarchical boundary structure (Not multiscale).\\ Problem: It is the same with Clockwork RNNs that boundary information is not explicit and expensive to be discovered.
+\item Hierarchical RNNs with Known explicit hierarchical boundary structure (Not multi-scale).\\ Problem: It is the same with Clockwork RNNs that boundary information is not explicit and expensive to be discovered.
 
@@
 \subsection{Update mechanism}
-They describe Hierarchical Multiscale RNN (HM-RNN) based on LSTM update rule. It is better to see the graph in paper.\\
+They describe Hierarchical Multi-scale RNN (HM-RNN) based on LSTM update rule. It is better to see the graph in paper.\\
 \marginpar{Why it is not based on RNN ?}
@@
 The result for character-level language model does not show clearly a good performance.
+
+%----------------------------------------------------------------------------------------
+%	Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation
+%----------------------------------------------------------------------------------------
+
+\section{Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation}
 
@@
 
-From now, the work of translation is modelling $p(f_1^J|e_1^I)$.
+From now, the work of translation is modeling $p(f_1^J|e_1^I)$.
 Our work is more complicated by adding an alignment component $a_1^J$ which maps from a source position j to a target position $a_j$ (It could be i, but there is also empty words).

### 2017-12-07 Paper_report.tex
Save

@@
 \usepackage{amsmath} % Required for some math elements 
+\usepackage[]{algorithm2e}
 
@@
 
-$ J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ] $
+\begin{equation}
+J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ]
+\label{Word Alignment Model Neural Network Gradient}
+\end{equation}
 
@@
 
+\section{HMM-NN Experiment}
+\subsection{Model 1: Simple NN-based Emission}
+We review the equation \eqref{Word Alignment Model Neural Network Gradient}.
+
+$
+J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad + p_{\theta'}(a_j, a_{j-1}|f_j) \, \bigtriangledown log \, p_{\theta}(a_j | a_{j-1})  ]
+$
+
+becomes
+
+\begin{equation}
+J(\theta) = \sum_{j=1}^J \sum_{a_j} p_{\theta'}(a_j|f_j) \, \bigtriangledown log \, p_{\theta}(f_j | e_{a_j}) \quad
+\end{equation}
+
+\begin{itemize}
+\item \textbf{Emission matrix }$p_{\theta}(f_j | e_{a_j})$: We receive the target-language sentence and return the probabilities for all source-language vocabulary under Feed-Forward NN.
+
+\item \textbf{Emission posterior} $p_{\theta'}(a_j|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages with size (J * I)
+
+\item \textbf{Transition matrix} $p_{\theta}(a_j | a_{j-1})$: This matrix does not depend on the source-language and the target-language sentence. It depends on a set of jump distance.
+	\begin{enumerate}
+	\item Initialize jump distance set.
+	\item Create transition matrix T with size (I * J) from this jump distance set.
+	\item Create initial transition matrix  T0 with size (1 * I) randomly
+	\item Calculate forward and backward message from NN-based emission matrix, transition matrix T and intial transition matrix T0.
+	\item Emission posterior is forward * backward message (See\cite{Tran16unsupervised})
+	\end{enumerate}
+\end{itemize}
+
+\begin{algorithm}[H]
+\textbf{Input:}\\
+	\begin{itemize}
+	\item Source sentence: $f_1^J = f_1,...,f_j,...f_J$
+	\item Target sentence: $e_1^I = f_1,...,f_i,...f_I$
+	\end{itemize}
+\textbf{Initialization:} \\
+	\begin{itemize}
+	\item Initialize jump distance set JD
+	\end{itemize}
+\textbf{Training:} \\
+\While{each sentence pair $(f_1^J, e_1^I)$ in Training set}{
+	\begin{enumerate}
+	\item Get Emission matrix E with size $(I * V_{F})$ from NN
+	\item Get Transition matrix T $(I * I)$ from \textbf{JD}
+	\item Select randomly Initial transition matrix T0 with $(1 * I)$
+	\item Get forward $\alpha$ and backward $\beta$ message with size $(J*I)$
+	\item Get Emission posterior $EP = \alpha * \beta $, Normalize EP and Reshape EP with size $(I * V_{F})$
+	\item Get expected-T $(I * I)$ from E, T, $\alpha$, $\beta$
+	\item Update \textbf{JD} from expected-T
+	\end{enumerate}
+
+ }
+ \textbf{Validation:} \\
+ \While{each sentence pair $(f_1^J, e_1^I)$ in Validation set}{
+	\begin{enumerate}
+	\item Get Emission matrix E with size $(I * V_{F})$ from NN
+	\item Get Transition matrix T $(2I * 2I)$ with Null tokens from \textbf{JD}
+	\item Select randomly Initial transition matrix T0 with $(1 * 2I)$
+	\item Get location pair $(J * 2I)$ with Viterbi from E with size $(2I * V_{F})$ and T with $(2I * 2I)$
+	\item Calculate AER
+	\end{enumerate}
+
+ }
+
+ \caption{Model 1}
+\end{algorithm}
+
 %----------------------------------------------------------------------------------------

### 2017-12-13 Paper_report.tex
New papers
Save

@@
 %----------------------------------------------------------------------------------------
-%	What does Attention in NMT pay Attention to ?
+%	Confidence through Attention
 %----------------------------------------------------------------------------------------
@@
 	t_{d}(a_{i}, a_{i-1}|e,f) = t_{d}(a_{i} - a_{i-1})
+	\label{Yang13word Alignment Translation Score}
 	\end{equation}
@@
 s_{NN}(a_1^ J|e_1^ I, f_1^ J) = \prod_{j = 1}^{J} t_{RNN}(a_{j}|a_1^{j-1},e_{a_{j}},f_j  )
+\label{Tamura14recurrent Alignment score}
 \end{equation}
@@
 %----------------------------------------------------------------------------------------
+%	Alignment-based Neural Machine Translation
+%----------------------------------------------------------------------------------------
+
+\section{Alignment-based Neural Machine Translation \citep{Alkhouli2016AlignmentBasedNM} }
+
+%----------------------------------------------------------------------------------------
 %	Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation
@@
 
-\section{Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation}
+\section{Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation \citep{Wang2017HybridNN} }
+The main idea is using NN for both alignment and lexicon model of HMM. These two models are trained jointly using the Baum-Welch algorithm.
+
+The experiment is not for word-based alignment but phrase-based translation, which increases 1\% of BLEU score.
+
+\subsection{NN-based Alignment and Lexical model}
+They define the alignment $b_{i} = i \rightarrow j $ (Not $a_{j} = j \rightarrow i $). Review the equation \eqref{Hidden Markov Alignment Model p(f, a|e)}. \\
+$p(e_1^I, b_1^I|f_1^J) = \prod_{i=1}^I p(e_i, b_i | b_1^{i-1}, e_1^{i-1}, f_1^J)
+$\\
+$ = \prod_{i=1}^I p( e_i | e_1^{i-1}, b_1^i, f_1^J) * p( b_i |b_1^{i-1}, e_1^{i-1}, f_1^J)
+$
+
+\begin{itemize}
+\item Alignment model: $p( b_i |b_1^{i-1}, e_1^{i-1},  f_1^J) = p(b_i - b_{i-1}| f^{b_{i-1} + \gamma m}_{b_{i-1} - \gamma m}, e_{i-n}^{i-1})$ \\
+where $\gamma m = \dfrac{m-1}{2}$ and n, m indicate window size.\\
+\marginpar{See Figure 1 in \citep{Wang2017HybridNN}}
+This lexical alignment model uses the context of $f^{b_{i-1}}$ and $e_i$.
+
+\item Lexical model: $p( e_i | e_1^{i-1}, b_1^{i}, f_1^J) = p(e_i|f^{b_{i} + \gamma m}_{b_{i} - \gamma m}, e_{i-n}^{i-1}  )$\\
+$= p(e_i| \: c(e_i),f^{b_{i} + \gamma m}_{b_{i} - \gamma m}, e_{i-n}^{i-1}) * p(c(e_i)|f^{b_{i} + \gamma m}_{b_{i} - \gamma m}, e_{i-n}^{i-1})$\\
+For this case, they apply class-factored output layer consisting a class layer (Class probability) and a word layer (Word probability for each class), which reduces the problem of large vocabulary.
+The word class is applied to target language $e$.
+\end{itemize}
+
+I rewrite under the notation of $a_{j}$.
+Review the equation \eqref{Hidden Markov Alignment Model p(f, a|e)}. \\
+$p(f_1^J, a_1^J|e_1^I) = \prod_{j=1}^J p(f_j, a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
+$\\
+$ = \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j |a_1^{j-1}, f_1^{j-1},  e_1^I)
+$
+
+\begin{itemize}
+\item Alignment model: $p( a_j |a_1^{j-1}, f_1^{j-1},  e_1^I) = p(a_j - a_{j-1}| e^{a_{j-1} + \gamma m}_{a_{j-1} - \gamma m}, f_{j-n}^{j-1})$ \\
+This lexical alignment model uses the context of $e^{a_{j-1}}$ and $f_j$.
+
+\item Lexical model: $p( f_j | f_1^{j-1}, a_j, e_1^I) = p(f_j|e^{a_{j} + \gamma m}_{a_{j} - \gamma m}, f_{j-n}^{j-1})  )$
+\marginpar{Class-factored output layer for target or source language ?}
+\end{itemize}
+
+\subsection{Objective function}
+
+\subsection{Algorithm}
+
+%----------------------------------------------------------------------------------------
+%	HMM Word and Phrase Alignment for Statistical Machine Translation
+%----------------------------------------------------------------------------------------
+
+\section{HMM Word and Phrase Alignment for Statistical Machine Translation \citep{Deng2008HMM} }
+
+%----------------------------------------------------------------------------------------
+%	Neural Network-based Word Alignment through Score Aggregation
+%----------------------------------------------------------------------------------------
+\section{Neural Network-based Word Alignment through Score Aggregation \citep{Legrand16neural}}
 
@@
 \begin{equation}
+p(f_1^J|e_1^I) = \sum_{a_1^J} p(f_1^J, a_1^J|e_1^I)
 \end{equation}
@@
 = p(J|e_1^I) \prod_{j=1}^J p( f_j | f_1^{j-1}, a_j, e_1^I) * p( a_j | f_1^{j-1}, a_1^{j-1}, e_1^I)
+\label{Hidden Markov Alignment Model p(f, a|e)}
 \end{equation}
@@
 \item Transition matrix $p_{\theta}(a_j | a_{j-1})$: We receive the target-language sentence and return this matrix.
+
 \item The posteriors $p_{\theta'}(a_j|f_j)$ and $p_{\theta'}(a_j, a_{j-1}|f_j)$ : We set source-language sentence as a set of observation, Baum-Welch algorithm returns forward and backward messages (How is the size of these messages)
@@
 
+\subsection{NN-based Alignment under jump-distance approach}
+\cite{Yang13word} recognize that the lexicalized distortion does not produce better alignment over the simple jump-distance based model (Not NN, randomly created), based on their experiment of small data.
+Therefore, they do not use target-language or source-language word for alignment.
+$t(a_{j}, a_{j-1}|e,f) = t(a_{j} - a_{j-1})$\\
+\marginpar{ See \eqref{Yang13word Alignment Translation Score} }
+
+\citep{Tamura14recurrent} continue the work of \citep{Yang13word} but reuse lexicalized distortion combined with RNN.
+$t(a_{j}, a_{j-1}|e,f) = t_{RNN}(a_{j} - a_{j-1}| a_{1}^{j-1}, f_j, e_{a_j})$\\
+\marginpar{See \eqref{Tamura14recurrent Alignment score}}
+One point important is that there is a different set of parameter for each distance.\\
+
+\citep{Alkhouli2016AlignmentBasedNM}, \citep{Wang2017HybridNN} use the context of $f_j$ and $e_{a_j}$. They do not use RNN, just simple FFNN.
+$p( a_j, a_{j-1}| f,  e) = p(a_{j} - a_{j-1}| e^{a_{j-1} + \gamma m}_{a_{j-1} - \gamma m}, f_{j-n}^{j-1})$ where $\gamma$, $n$ are window sizes.
+
 \section{Symmetrical alignment}
@@
 \section{Techniques in Alignment}
+\subsection{Agreement between models}
 
-\subsection{Agreement between models}
+\subsection{Word class for large vocabulary}
 
